Analysis of split plot design using MCMCglmm

### 2017-06-16 Analysis.Rmd
Add headers and flesh out the conclusions

@@

@@

### Tiller Sheath Blight Incidence

In 2015 the highest N treatment was significant, in 2016 the lowest N rates were significant.

>>>>

### 2015 Leaf Sheath Blight Severity Model

@@

### 2016 Leaf Sheath Blight Severity Model

@@

### Tiller Sheath Blight Incidence and Severity

In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity.

### Leaf Sheath Blight Severity

In neither experiment was the leaf sheath blight affected by nitrogen rates or irrigation regime.

### Interactions of Nitrogen and Irrigation Regime

In neither experiment was the interaction of nitrogen with irrigation regime significant.

### Model Fit
